### 2016-07-10 Projects/DelCo_2012/Report/DelCo_2012.tex
Mods to MCFRS in Acknowledgements

Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study. The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Bryan Rojtas, Chris Reilly, Sean Regan, Alan Butsch, Ralph Thomas, Daniel Hudson, Michael Johns, and Douglas Wallace.

>>>>

Thank you to Chief Scott Goldstein and former Chief Steve Lohr of the Montgomery County (MD) Fire and Rescue Service for their support of this study. The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Alan Butsch, Daniel Hudson, Michael Johns, Steven Neubauer, Curtis Poole, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph Thomas, and Douglas Wallace.
